Alleviating Topology Mismatch in Distributed Overlay Networks: A Survey

### 2014-01-27 unstructured.tex
2012.10.24 (Vassilis) Changed paper title. Text reworked (content clarifications added, typos corrected, broken references fixed).

This section is dedicated to the unstructured P2P architectures. In the next
paragraphs,algorithms for tackling the topology mismatch problem on such
networks are discussed, analysed and categorised based on the use of the
overlay structure, message forwarding approach for peer communication and
techniques proposed for detecting proximity in order to optimise overlay
topology.

@@

% BROADCAST OPTIMISATION

@@

The directed BFS%, as shown in Figure~\ref{figure:dbfs:dbfs},
tries to avoid this delay by forwarding the query messages only to a selected
set of neighbours, in which the selection criteria varies from the number of
results received previously, distance in terms of hops, bandwidth, or the query
load of the neighbour.

@@

% \begin{center}
% \begin{tabular}{ccc}
% \textbf{Efficiency} & \textbf{Overhead} & \textbf{Scalability} \\
% \hline
% Iterative Deepening & ? & ? & ?
% Directed BFS & ? & ? & ?
% Local Indices & ? & ? & ?
% \end{tabular}
% \end{center}
\begin{center}
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Iterative Deepening} &
% needs recalculation in every iteration step
% extra delay imposed in a high churn environment that prohibits the algorithm
% to start from the last level of nodes and results in a restart of the whole
% process
low &
% the process in not started from the begining at each iteration step
low &
% 
medium \\
\emph{Directed BFS} &
% Better time to satisfaction compared to iterative deepening
medium &
% Better quality and quicker results mean more aggregate bandwidth and
% processing power needs to be consumed since more nodes are involved (death
% spirral).
medium &
% BFS is Gnutella's non efficient communcation method
medium \\
\emph{Local Indices} &
% efficiency is enhanced greatly since data pointers are replicated across the
% network
high &
% updating indices is a time and resource consuming process.
medium &
% the scalability is constrained by the indices update in a highly dynamic
% environment (high churn)
medium \\
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{ \bf Delay Aware P2P System}
A new \emph{Delay Aware P2P System (DAPS)} is introduced in \cite{ZL2005}. Its
main goal is to reduce the time of a look-up request by dividing the routing
tables of peers into several sectors of increasing delay. The source node
emitting the query message defines a delay boundary or the \emph{pruning
factor} in the paper's context. Request messages are then forwarded only to
nodes whose delay is less than or equal that boundary. With the clustered
routing tables and the loose organisation of DAPS' overlay network it is
considered by is between structured and unstructured.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Gia}
\emph{Gia} \cite{CRBLS2003} is an effort to solve the scalability
problem of the unstructured P2P file sharing systems, in particular Gnutella.
The main novelty in the design of Gia is the replacement of the blind flooding
approach of Gnutella with random walks \cite{lv_randomwalks_2002}. Although
random walks is a step in the right direction, issuing only a single copy of the
query within the network reduces the search scope, thus affecting negatively the
success rate of the query.  In order to overcome this limitation, Gia introduces
a token-based flow control mechanism, which is essentially an intelligent flow
control algorithm that gradually redirects the queries to nodes which are more
likely to answer. In order to prevent overloading of nodes with query requests,
Gia uses a token-based flow control algorithm in which each node announces the
number of query requests it can handle in terms of tokens to its neighbours, so
that neighbours only forward query requests to nodes that they previously
received tokens from. Gia also acknowledges the heterogenity in peer bandwidth,
processing power, disk speed, etc, of the nodes in P2P networks and uses this
information when connecting nodes to each other and by using a topology
adaptation algorithm, Gia ensures that high capacity nodes have high degrees and
low capacity nodes are within short proximity to high capacity ones.
% TODO: THIS FOLLOWING REMARK SOUNDS LIKE THE ALGORITHM SHOULDN'T BE IN THIS
%       SURVEY AFTER ALL!!
Although the topology adaptation algorithm Gia uses improves the scalability of
the network, it does not help much in solving the topology mismatch problem,
since it does not consider the underlying physical topology.

%
%More specifically, there are four key components in the design of
%\emph{Gia} which are summarized bellow:
%\begin{enumerate}
%  \item A \emph{dynamic topology adaptation} protocol that puts
%participating nodes within short reach of high capacity nodes so that these
%\emph{high-degree} nodes, which due to their high connectivity receive most of
%the queries, actually have the capacity to handle them.
%  \item An \emph{active flow control} scheme is used to avoid overloaded
% hot-spots. Heterogeneity is detected and flow control tokens are given to
%nodes based on the available capacity.
%  \item Every node maintains pointers to to the content that is offered by
% their immediate neighbours, creating a \emph{one-hop replication} of pointers,
%scheme.
%  \item A \emph{search protocol} based on random walks, that is biased towards
% directing queries to high-capacity nodes that are typically best able to
%answer these queries.
%\end{enumerate}
%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Distributed Cycle Minimization Protocol (DCMP)}
We have already discussed that blind flooding mechanism broadcasts messages with
no real targeting, many times to a direction far from the path that can
ultimatelly fullfil the query request. Another problem with topology unaware
systems is the duplication of messages due to cycles, even along the correct
forwarding path. The authors of \cite{ZKB2008} fucused on that exact deficiency
of overlay networks and introduced Distributed Cycle Minimization Protocol
(DCMP), a dynamic, fully distributed method to remove cycles without sacrificing
overlay connectivity, resilience and other important properties of unstructured
architectures by avoiding a hierarchical organisation of peers. In DCMP, once a
cycle is detected, the most powerful node in that cycle is elected as the
\emph{Gate Peer} and the cycle is then broken at a strategic place so that it
will result in the minimisation of the distance between the Gate Peer and all
other nodes that participated in that cycle. The process is managed by using two
special message types namely \emph{Information Collection (IC)} and \emph{Cut
Message (CM)}. One disadvantage of DCMP is that since the distance a forwarded
message can travel is limited by the TTL value, which is practically $7$ in most
cases DCMP cannot detect cycles formed by more than 7 peers. Even though cycle
elimination improves the network performance, it does not actually solve the
topology mismatch problem.

%
%\subsection{Distributed Cycle Minimization Protocol}
%
%\paragraph{}
%The first step after detecting a duplicate message by some peer is to gather
% information from all peers in the cycle using a new type of control message
%called \emph{Information Collecting Message} or \emph{ICM}. ICM contains:
%\begin{inparaenum}[\itshape i\upshape)]
%  \item a \emph{GUID}\footnote{Globally Unique IDentifier assigned to every
% query message generated by any node.} field same as the one of the duplicate
%message,
%  \item \emph{DetectionID} field which represents the direction of the
% connection where the duplicate was identified\footnote{This ensures the
%uniqueness of the ICM messages because as it travels through many cyclic paths,
%multiple peers will detect the duplicates and initiate an ICM message.}, and
%  \item \emph{Node Information Vector (NIV)} which contains information
% (bandwidth, CPU power, etc) about peers that propagated the ICM.
%\end{inparaenum}
%
%\paragraph{}
%Suppose $A$ detected the duplicate as depicted in Figure~\ref{figure:dcmp}. It
% then emits an ICM to $B$ and $F$, that initially contains information only
%about itself. Each peer that receives the ICM, appends its information and
%propagates it along the reverse path of the original message. Since two copies
%of ICM are sent, at some point, a peer, say peer $D$, will receive a duplicate
%ICM. Using the information in the NIVs of the ICMs, $D$, decides to cut (for
%example) the EF connection. To inform the other peers about its decision, it
%emits a \emph{Cut Message (CM)} which contains the GUID and DetectionID of the
%corresponding ICM and an additional field that identifies the connection to be
%cut. $D$, then, forwards the CM in the reverse directions from where the ICM
%arrived. Similarly CMs received by any peer are propagated toward the reverse
%path of the corresponding ICM. Eventually, either peer $E$ or peer $F$ will
%receive the CM and cut the connection, thus eliminating the cycle.
%
%Receiving a duplicate ICM denotes the existence of a cycle. The opposite is not
% true though. For example, if the cycle contains $2 \times TTL$ edges, it will
%not be detected, because the ICM messages will be discarded before they locate
%it. There is a tradeoff between preserving the connectivity of the network and
%minimizing the duplicates that makes such a possibility to be safely ignored.
%
%\begin{figure}
%\centering
%  \includegraphics[scale=0.4]{img/dcmp.jpeg}
%\caption{Cycle elimination methods in DCMP}
%\label{figure:dcmp}
%\end{figure}
%
%\paragraph{}

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It return more result than LTM according to experiments in
% \cite{ZKB2008}
medium &
% Duplicates are an important fraction of the redundant overhead imposed by
% topology mismatch and thus DCMP minimises this as possible.
% The control overhead is also one to two orders of magnitude less than LTM due
% to its ``lazy'' broadcasting of control messages (as opposed to LTM's periodic
% approach) - \cite{ZKB2008}
low &
% fully distributed method
high
\end{tabular}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Replication Strategies in Unstructured Peer-to-Peer Networks}
\cite{CS2002} aim to improve the inefficient blind search algorithm by
replicating the data in a P2P network. The main intuition behind the
idea of replication, or using cached copies, is that as the number of copies for
each item increases in the network, it would be easier for a search algorithm,
even a random one, to locate these items. In order to analyse the feasibility of
such an approach, the authors investigate three different replication
strategies, namely uniform, proportional, and square root allocation. In the
uniform model, the copies of items are uniformly replicated in the network,
while in the proportional model, the items are replicated based on their query
rate, so that frequently queried items are replicated more. The square root
allocation is a strategy proposed in this paper, which is a model between the
uniform and proportional allocation.  In order to evaluate the outcome of the
replication models, the overall costs of successful and unsuccessful searches in
the network are compared. Results argue that the uniform allocation model
minimizes the maximum search size, therefore reduces the time spent on an
unsuccessful search. The proportional model, on the other hand, promotes the
more frequently queried items by replicating them more, therefore decreases the
search time for popular items, but suffers when needing to locate the rare
items. The authors also claim that the expected successful search size is the
same for uniform and proportional models, and any approach between them would
always behave much better. Therefore they propose the square root allocation
approach, which is a replication strategy that minimizes the expected search
size of successful queries in P2P networks.

\begin{center}
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Uniform Replication} &
% Proportional and Uniform are the worst “reasonable” strategies
low &
% When item is created, replicate its key in a fixed number of hosts.
low &
%
medium \\
\emph{Proportional Replication} &
% Proportional and Uniform are the worst “reasonable” strategies
low &
% for each query, replicate the key in a fixed number of hosts (need to know or
% estimate the query rate)
medium &
%
low \\
\emph{Square Root Replication Allocation} &
% All (strictly) in-between strategies are (strictly) better than Uniform and
% Proportional - replication theory
medium &
% Assuming that each query keeps track of the search size then each time a query
% is finished the object is copied to a number of sites proportional to the
% number of probes that the search required.
medium &
% e.g. path replication is easy to scale, just detect the path along which the
% query ultimatelly got fulfilled
medium \\
\end{tabular}
\end{center}

@@

%       OVERLAY OPTIMISATION

@@

% \begin{figure}[ht]
% \centering
% \subfigure[Underlying network with edge costs.] {
%   \includegraphics[scale=0.4]{img/algorithms/narada}
%   \label{figure:narada:underlying}
% }\qquad\qquad
% \subfigure[Peer A sends a message to the rest using regular broadcast.] {
%   \includegraphics[scale=0.4]{img/algorithms/narada2}
%   \label{figure:narada:regu}
% }\qquad\qquad
% \subfigure[Peer A sends a message to the rest using end system multicast.] {
%   \includegraphics[scale=0.4]{img/algorithms/narada3}
%   \label{figure:narada:multicast}
% }
% \caption{A visualisation of the Narada protocol.}
% \label{figure:narada}
% \end{figure}

\emph{Narada} \cite{CRZ2000,CRSZ2001,CRSZ2002} is a generic
protocol for creating self-adapting overlay networks, that can achieve
application-layer multicast communication without requiring IP multicast
infrastructure at the network layer\footnote{
  IP multicast is the term reffering to the method of sending IP datagrams to a
  group of receivers in a single transmission. Even though the method is
  available some years now, IP multicast has not taken off as anticipated since
  many believe that it violates the stateless design of the current Internet.
  For this reason it is widely deployed in contained environments like
  enterprises (i.e. IPTV applications - distance learning, video conferencing),
  commercial stock exchanges, and multimedia content delivery networks.
}. Although it was not originally designed as a P2P system nor can be considered
scalable in the contemporary sense of the term, Narada has been pioneering
(maybe along with \emph{Scattercast} \cite{C2000}) in that
it was the first to consider the feasibility of overlay-based, application
layer, services over the Internet that can take into account bandwidth and
latency properties of the physical underlying infrastructure. Additionally,
authors realised the inefficiency caused by the topology mismatch problem and
tried to encounter it by building a richer connected graph, called a
\emph{mesh}, and building per source minimum spanning trees\footnote{
  ENarada \cite{LYL2008} used Gossip protocol for the
construction
}.
%as shown in Figure~\ref{figure:narada}.
They also keep the graph and the trees
dynamically updated while nodes continue to join and leave the network.
Moreover, the protocol tries to ease the physical link stress, the overall
resource usage and the relative delay among end systems. Unfortunately, the most
important limitation of Narada is that although it works reasonably well for
small groups, it does not scale well for larger networks, therefore it is not
suitable for, potentially very large, P2P file sharing application networks.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Adaptive Overlay Topology Optimization (AOTO)}
\emph{Adaptive Overlay Topology Optimization (AOTO)} \cite{LZXN2003} is one
of the first attempts, along with Narada, to address the topology mismatch
problem. AOTO is a distributed algorithm that works in two steps, namelly
\emph{Selective Flooding} and \emph{Active Topology} to optimize the usage of
the underlying physical resourses. In \emph{Selective Flooding} a minimum
spanning tree is built among each peer and its immediate neighbours so that
queries are not flooding the whole network and at the same time without
shrinking the search scope. During \emph{Active Topology}, the overlay
links are revised so that they depict the physical network topology as close as
possible. This is done independently, by each peer by replacing non-flooding
neighbours, with closer nodes. Picking a replacement out of these non-fooding
neighbours follows a random policy (called \emph{Randomized AT} algorithm in the
paper's context). For these steps a peer needs to keep track of communication
costs to all its neighbours (e.g. the network delay) as well as between any
pair of neighbours (meaning also that additional, cost probing, message types
need to be added to the Gnutella protocol). Whenever a new neighbour cost table
is received or there is a change of neighbours, the source peer has to
re-calculate the multicast tree and apply the randomized AT algorithm.

%\paragraph*{Selective Flooding (SF)}
%
% TODO: I DON'T REMEMBER WHY THE FOLLOWING IS MENTIONING LTM WHICH IS ANOTHER
%       ALGORITM. MAYBE THIS CAN BE USED AS A PART OF DISCUSSION AND/OR
%       COMPARISON OF AOTO AND LTM
% TODO: EDIT: LTM SEEMS A MISTAKE HERE BETTER NOT USE IT FOR DISCUSSION (THIS
%             IS AOTO)
%LTM's SF effectiveness has be proven to be detached from the different physical
% or overlay topologies. On the other hand, SF is more effective with large
%number of logical neighbours. It can reach an average optimization rate of 87.4
%percent on a logical topology with an average of 30 logical neighbours.
%
%\paragraph*{Active Topology (AT)}
%
%Different numbers of average logical neighbours has little to do with the
% effectiveness of AT. If the source has $n$ non-flooding peers, there are $n$
%potential neighbour replacements. The overhead to exhaust all $n$ possible
%replacements can be high, so in practice, after each replacement the source
%peer can decide whether it needs to find another candidate peer. This is done
%by computing the cost improvement ratio greater than some predefined
%termination threshold. The larger the threshold, the slower, in the number of
%optimization steps, the reduction of the normalized average distance. As a
%whole the average response time is significantly reduced when more optimization
%steps taken.

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
%
medium &
% tracking of communication costs to all peer's neighbours as well as between
% any pair of neighbours. Whenever a new neighbour cost table is received or
% there is a change of neighbours, the source peer has to re-calculate the
% multicast tree and apply the randomized AT algorithm.
high &
% needs global knowledge
medium
\end{tabular}
\end{center}

>>>>

This section is dedicated to the unstructured P2P architectures. In the next
paragraphs, algorithms for tackling the topology mismatch problem on such
networks are discussed, analyzed and categorized based on the use of the
overlay structure, message forwarding approach for peer communication and
techniques proposed for detecting proximity in order to optimize overlay
topology.

@@

% BROADCAST OPTIMIZATION

@@

The directed BFS%, as shown in Figure~\ref{figure:dbfs:dbfs},
tries to avoid this delay by forwarding the query messages only to a selected
set of neighbors, in which the selection criteria varies from the number of
results received previously, distance in terms of hops, bandwidth, or the query
load of the neighbor.

@@

% \begin{center}
% \begin{tabular}{ccc}
% \textbf{Efficiency} & \textbf{Overhead} & \textbf{Scalability} \\
% \hline
% Iterative Deepening & ? & ? & ?
% Directed BFS & ? & ? & ?
% Local Indices & ? & ? & ?
% \end{tabular}
% \end{center}
\begin{center}
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Iterative Deepening} &
% needs recalculation in every iteration step
% extra delay imposed in a high churn environment that prohibits the algorithm
% to start from the last level of nodes and results in a restart of the whole
% process
low &
% the process in not started from the beginning at each iteration step
low &
% 
medium \\
\emph{Directed BFS} &
% Better time to satisfaction compared to iterative deepening
medium &
% Better quality and quicker results mean more aggregate bandwidth and
% processing power needs to be consumed since more nodes are involved (death
% spirral).
medium &
% BFS is Gnutella's non efficient communication method
medium \\
\emph{Local Indices} &
% efficiency is enhanced greatly since data pointers are replicated across the
% network
high &
% updating indices is a time and resource consuming process.
medium &
% the scalability is constrained by the indices update in a highly dynamic
% environment (high churn)
medium \\
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{ \bf Delay Aware P2P System}
A new \emph{Delay Aware P2P System (DAPS)} is introduced in \cite{ZL2005}. Its
main goal is to reduce the time of a look-up request by dividing the routing
tables of peers into several sectors of increasing delay. The source node
emitting the query message defines a delay boundary or the \emph{pruning
factor} in the paper's context. Request messages are then forwarded only to
nodes whose delay is less than or equal that boundary. With the clustered
routing tables and the loose organization of DAPS' overlay network it is
considered by is between structured and unstructured.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Gia}
\emph{Gia} \cite{CRBLS2003} is an effort to solve the scalability
problem of the unstructured P2P file sharing systems, in particular Gnutella.
The main novelty in the design of Gia is the replacement of the blind flooding
approach of Gnutella with random walks \cite{lv_randomwalks_2002}. Although
random walks is a step in the right direction, issuing only a single copy of the
query within the network reduces the search scope, thus affecting negatively the
success rate of the query.  In order to overcome this limitation, Gia introduces
a token-based flow control mechanism, which is essentially an intelligent flow
control algorithm that gradually redirects the queries to nodes which are more
likely to answer. In order to prevent overloading of nodes with query requests,
Gia uses a token-based flow control algorithm in which each node announces the
number of query requests it can handle in terms of tokens to its neighbors, so
that neighbors only forward query requests to nodes that they previously
received tokens from. Gia also acknowledges the heterogeneity in peer bandwidth,
processing power, disk speed, etc, of the nodes in P2P networks and uses this
information when connecting nodes to each other and by using a topology
adaptation algorithm, Gia ensures that high capacity nodes have high degrees and
low capacity nodes are within short proximity to high capacity ones.
% TODO: THIS FOLLOWING REMARK SOUNDS LIKE THE ALGORITHM SHOULDN'T BE IN THIS
%       SURVEY AFTER ALL!!
Although the topology adaptation algorithm Gia uses improves the scalability of
the network, it does not help much in solving the topology mismatch problem,
since it does not consider the underlying physical topology.

%
%More specifically, there are four key components in the design of
%\emph{Gia} which are summarized bellow:
%\begin{enumerate}
%  \item A \emph{dynamic topology adaptation} protocol that puts
%participating nodes within short reach of high capacity nodes so that these
%\emph{high-degree} nodes, which due to their high connectivity receive most of
%the queries, actually have the capacity to handle them.
%  \item An \emph{active flow control} scheme is used to avoid overloaded
% hot-spots. Heterogeneity is detected and flow control tokens are given to
%nodes based on the available capacity.
%  \item Every node maintains pointers to to the content that is offered by
% their immediate neighbors, creating a \emph{one-hop replication} of pointers,
%scheme.
%  \item A \emph{search protocol} based on random walks, that is biased towards
% directing queries to high-capacity nodes that are typically best able to
%answer these queries.
%\end{enumerate}
%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Distributed Cycle Minimization Protocol (DCMP)}
We have already discussed that blind flooding mechanism broadcasts messages with
no real targeting, many times to a direction far from the path that can
ultimately fulfill the query request. Another problem with topology unaware
systems is the duplication of messages due to cycles, even along the correct
forwarding path. The authors of \cite{ZKB2008} focused on that exact deficiency
of overlay networks and introduced Distributed Cycle Minimization Protocol
(DCMP), a dynamic, fully distributed method to remove cycles without sacrificing
overlay connectivity, resilience and other important properties of unstructured
architectures by avoiding a hierarchical organization of peers. In DCMP, once a
cycle is detected, the most powerful node in that cycle is elected as the
\emph{Gate Peer} and the cycle is then broken at a strategic place so that it
will result in the minimization of the distance between the Gate Peer and all
other nodes that participated in that cycle. The process is managed by using two
special message types namely \emph{Information Collection (IC)} and \emph{Cut
Message (CM)}. One disadvantage of DCMP is that since the distance a forwarded
message can travel is limited by the TTL value, which is practically $7$ in most
cases DCMP cannot detect cycles formed by more than 7 peers. Even though cycle
elimination improves the network performance, it does not actually solve the
topology mismatch problem.

%
%\subsection{Distributed Cycle Minimization Protocol}
%
%\paragraph{}
%The first step after detecting a duplicate message by some peer is to gather
% information from all peers in the cycle using a new type of control message
%called \emph{Information Collecting Message} or \emph{ICM}. ICM contains:
%\begin{inparaenum}[\itshape i\upshape)]
%  \item a \emph{GUID}\footnote{Globally Unique Identifier assigned to every
% query message generated by any node.} field same as the one of the duplicate
%message,
%  \item \emph{DetectionID} field which represents the direction of the
% connection where the duplicate was identified\footnote{This ensures the
%uniqueness of the ICM messages because as it travels through many cyclic paths,
%multiple peers will detect the duplicates and initiate an ICM message.}, and
%  \item \emph{Node Information Vector (NIV)} which contains information
% (bandwidth, CPU power, etc) about peers that propagated the ICM.
%\end{inparaenum}
%
%\paragraph{}
%Suppose $A$ detected the duplicate as depicted in Figure~\ref{figure:dcmp}. It
% then emits an ICM to $B$ and $F$, that initially contains information only
%about itself. Each peer that receives the ICM, appends its information and
%propagates it along the reverse path of the original message. Since two copies
%of ICM are sent, at some point, a peer, say peer $D$, will receive a duplicate
%ICM. Using the information in the NIVs of the ICMs, $D$, decides to cut (for
%example) the EF connection. To inform the other peers about its decision, it
%emits a \emph{Cut Message (CM)} which contains the GUID and DetectionID of the
%corresponding ICM and an additional field that identifies the connection to be
%cut. $D$, then, forwards the CM in the reverse directions from where the ICM
%arrived. Similarly CMs received by any peer are propagated toward the reverse
%path of the corresponding ICM. Eventually, either peer $E$ or peer $F$ will
%receive the CM and cut the connection, thus eliminating the cycle.
%
%Receiving a duplicate ICM denotes the existence of a cycle. The opposite is not
% true though. For example, if the cycle contains $2 \times TTL$ edges, it will
%not be detected, because the ICM messages will be discarded before they locate
%it. There is a trade-off between preserving the connectivity of the network and
%minimizing the duplicates that makes such a possibility to be safely ignored.
%
%\begin{figure}
%\centering
%  \includegraphics[scale=0.4]{img/dcmp.jpeg}
%\caption{Cycle elimination methods in DCMP}
%\label{figure:dcmp}
%\end{figure}
%
%\paragraph{}

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It return more result than LTM according to experiments in
% \cite{ZKB2008}
medium &
% Duplicates are an important fraction of the redundant overhead imposed by
% topology mismatch and thus DCMP minimizes this as possible.
% The control overhead is also one to two orders of magnitude less than LTM due
% to its ``lazy'' broadcasting of control messages (as opposed to LTM's periodic
% approach) - \cite{ZKB2008}
low &
% fully distributed method
high
\end{tabular}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Replication Strategies in Unstructured Peer-to-Peer Networks}
\cite{CS2002} aim to improve the inefficient blind search algorithm by
replicating the data in a P2P network. The main intuition behind the
idea of replication, or using cached copies, is that as the number of copies for
each item increases in the network, it would be easier for a search algorithm,
even a random one, to locate these items. In order to analyze the feasibility of
such an approach, the authors investigate three different replication
strategies, namely uniform, proportional, and square root allocation. In the
uniform model, the copies of items are uniformly replicated in the network,
while in the proportional model, the items are replicated based on their query
rate, so that frequently queried items are replicated more. The square root
allocation is a strategy proposed by Cohen and Shenker, which is a model between
the uniform and proportional allocation.  In order to evaluate the outcome of
the replication models, the overall costs of successful and unsuccessful
searches in the network are compared. Results argue that the uniform allocation
model minimizes the maximum search size, therefore reduces the time spent on an
unsuccessful search. The proportional model, on the other hand, promotes the
more frequently queried items by replicating them more, therefore decreases the
search time for popular items, but suffers when needing to locate the rare
items. The authors also claim that the expected successful search size is the
same for uniform and proportional models, and any approach between them would
always behave much better. Therefore they propose the square root allocation
approach, which is a replication strategy that minimizes the expected search
size of successful queries in P2P networks.

\begin{center}
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Uniform Replication} &
% Proportional and Uniform are the worst “reasonable” strategies
low &
% When item is created, replicate its key in a fixed number of hosts.
low &
%
medium \\
\emph{Proportional Replication} &
% Proportional and Uniform are the worst “reasonable” strategies
low &
% for each query, replicate the key in a fixed number of hosts (need to know or
% estimate the query rate)
medium &
%
low \\
\emph{Square Root Replication Allocation} &
% All (strictly) in-between strategies are (strictly) better than Uniform and
% Proportional - replication theory
medium &
% Assuming that each query keeps track of the search size then each time a query
% is finished the object is copied to a number of sites proportional to the
% number of probes that the search required.
medium &
% e.g. path replication is easy to scale, just detect the path along which the
% query ultimately got fulfilled
medium \\
\end{tabular}
\end{center}

@@

%       OVERLAY OPTIMIZATION

@@

% \begin{figure}[ht]
% \centering
% \subfigure[Underlying network with edge costs.] {
%   \includegraphics[scale=0.4]{img/algorithms/narada}
%   \label{figure:narada:underlying}
% }\qquad\qquad
% \subfigure[Peer A sends a message to the rest using regular broadcast.] {
%   \includegraphics[scale=0.4]{img/algorithms/narada2}
%   \label{figure:narada:regu}
% }\qquad\qquad
% \subfigure[Peer A sends a message to the rest using end system multi-cast.] {
%   \includegraphics[scale=0.4]{img/algorithms/narada3}
%   \label{figure:narada:multicast}
% }
% \caption{A visualization of the Narada protocol.}
% \label{figure:narada}
% \end{figure}

\emph{Narada} \cite{CRZ2000,CRSZ2001,CRSZ2002} is a generic
protocol for creating self-adapting overlay networks, that can achieve
application-layer multi-cast communication without requiring IP multi-cast
infrastructure at the network layer\footnote{
  IP multi-cast is the term referring to the method of sending IP datagrams to a
  group of receivers in a single transmission. Even though the method is
  available some years now, IP multi-cast has not taken off as anticipated since
  many believe that it violates the stateless design of the current Internet.
  For this reason it is widely deployed in contained environments like
  enterprises (i.e. IPTV applications - distance learning, video conferencing),
  commercial stock exchanges, and multimedia content delivery networks.
}. Although it was not originally designed as a P2P system nor can be considered
scalable in the contemporary sense of the term, Narada has been pioneering
(maybe along with \emph{Scattercast} \cite{C2000}) in that
it was the first to consider the feasibility of overlay-based, application
layer, services over the Internet that can take into account bandwidth and
latency properties of the physical underlying infrastructure. Additionally,
authors realized the inefficiency caused by the topology mismatch problem and
tried to encounter it by building a richer connected graph, called a
\emph{mesh}, and building per source minimum spanning trees\footnote{
  ENarada \cite{LYL2008} used Gossip protocol for the
construction
}.
%as shown in Figure~\ref{figure:narada}.
They also keep the graph and the trees
dynamically updated while nodes continue to join and leave the network.
Moreover, the protocol tries to ease the physical link stress, the overall
resource usage and the relative delay among end systems. Unfortunately, the most
important limitation of Narada is that although it works reasonably well for
small groups, it does not scale well for larger networks, therefore it is not
suitable for, potentially very large, P2P file sharing application networks.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Adaptive Overlay Topology Optimization (AOTO)}
\emph{Adaptive Overlay Topology Optimization (AOTO)} \cite{LZXN2003} is one
of the first attempts, along with Narada, to address the topology mismatch
problem. AOTO is a distributed algorithm that works in two steps, namely
\emph{Selective Flooding} and \emph{Active Topology} to optimize the usage of
the underlying physical resources. In \emph{Selective Flooding} a minimum
spanning tree is built among each peer and its immediate neighbors so that
queries are not flooding the whole network and at the same time without
shrinking the search scope. During \emph{Active Topology}, the overlay
links are revised so that they depict the physical network topology as close as
possible. This is done independently, by each peer by replacing non-flooding
neighbors, with closer nodes. Picking a replacement out of these non-flooding
neighbors follows a random policy (called \emph{Randomized AT} algorithm in the
paper's context). For these steps a peer needs to keep track of communication
costs to all its neighbors (e.g. the network delay) as well as between any
pair of neighbors (meaning also that additional, cost probing, message types
need to be added to the Gnutella protocol). Whenever a new neighbor cost table
is received or there is a change of neighbors, the source peer has to
re-calculate the multi-cast tree and apply the randomized AT algorithm.

%\paragraph*{Selective Flooding (SF)}
%
% TODO: I DON'T REMEMBER WHY THE FOLLOWING IS MENTIONING LTM WHICH IS ANOTHER
%       ALGORITM. MAYBE THIS CAN BE USED AS A PART OF DISCUSSION AND/OR
%       COMPARISON OF AOTO AND LTM
% TODO: EDIT: LTM SEEMS A MISTAKE HERE BETTER NOT USE IT FOR DISCUSSION (THIS
%             IS AOTO)
%LTM's SF effectiveness has be proven to be detached from the different physical
% or overlay topologies. On the other hand, SF is more effective with large
%number of logical neighbors. It can reach an average optimization rate of 87.4
%percent on a logical topology with an average of 30 logical neighbors.
%
%\paragraph*{Active Topology (AT)}
%
%Different numbers of average logical neighbors has little to do with the
% effectiveness of AT. If the source has $n$ non-flooding peers, there are $n$
%potential neighbor replacements. The overhead to exhaust all $n$ possible
%replacements can be high, so in practice, after each replacement the source
%peer can decide whether it needs to find another candidate peer. This is done
%by computing the cost improvement ratio greater than some predefined
%termination threshold. The larger the threshold, the slower, in the number of
%optimization steps, the reduction of the normalized average distance. As a
%whole the average response time is significantly reduced when more optimization
%steps taken.

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
%
medium &
% tracking of communication costs to all peer's neighbors as well as between
% any pair of neighbors. Whenever a new neighbor cost table is received or
% there is a change of neighbors, the source peer has to re-calculate the
% multi-cast tree and apply the randomized AT algorithm.
high &
% needs global knowledge
medium
\end{tabular}
\end{center}
